---
title: "HW5 notebook"
output: html_notebook
---

Here is the first method for overlaying shape data on a raster.

Use the following packages (install them first), then use them via
the library() call: tmap, tmaptools, rgdal, sp, OpenStreetMap, osmdata

These calls are useful: readOGR(), tmaptools::read_osm(),
tm_shape(), tm_raster(), tm_dots()

1. readOGR() your shapefile, store it in a var
2. read_osm() the bbox of #1 above, store it in a var
3. do tm_shape() on #2 + tm_raster() +
tm_shape() on #1 + tm_dots() to specify point color and size

```{r}
#Uncomment and run installation commands mentioned below if packages are not present.

#install.packages("tmap")
#install.packages("tmaptools")
#install.packages("rgdal")
#install.packages("sp")
#install.packages("OpenStreetMap")
#install.packages("osmdata")

#load and attach the installed packages using library
library("tmap")
library("tmaptools")
library("rgdal")
library("sp")
library("OpenStreetMap")
library("osmdata")

# Read .shp file by providing the path where it is stored.
myfile = readOGR("/Users/mahimasinghdeo/Downloads/mygeodata/new.shp")
#Read Open Street Map Data of the bounding box using read_osm()
mybox = read_osm(myfile)
#tm_shape specifies the shape object. tm_raster draws a raster for it. 
#tm_dots draws dots on the shape provided. Colour and size of dots have been set. 
tm_shape(mybox)+tm_raster()+tm_shape(myfile)+tm_dots(size = 2.3, col = "red") 





```

And here's the second.

Use these packages: PBSmapping, ggmap
And these calls: importShapefile(), as.data.frame(), get_map(), ggmap(), 
geom_point()

1. importShapefile() into a var
2. convert it (#1 above) to a dataframe, store it in a var
3. get_map() with a location that's in your collection of (lat,long),
store it in a var
4. do ggmap() on #3, + geom_point() on #2

```{r}
#Uncomment and run installation commands mentioned below if packages are not present.

#install.packages("PBSmapping")
#install.packages("ggmap")

#load and attach the installed packages using library
library("PBSmapping")
library("ggmap")

# Import .shp file by providing the path where it is stored.
myfile2 = importShapefile("/Users/mahimasinghdeo/Downloads/mygeodata/new.shp")
#Convert .shp file data to a dataframe.
mydataframe = as.data.frame(myfile2)
#Get a map for the coordinates mentioned. A zoom level has been set.
mylocation = get_map(location = c(-118.2802,34.0230), zoom=16)
#ggmap() plots a raster for the map obtained. 
#geom_point() creates a scatterplot for points in dataframe. Size and colour have been set.
ggmap(mylocation) + geom_point( data = mydataframe, aes(X,Y), size =1.5, col="red")
```